### 2021-11-21 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@9b02b7174adf7731fc95d2491dc7fc5b4108c618 🚀

As the data we have is spatially sparse and likely to contain many
interaction ``false-negatives'' (Strydom \emph{et al.} 2021b), we begin
by predicting a metaweb of interactions across Colorado as they exist
\emph{in the present}. We do this using a set of candidate interaction
prediction models: relative abundance only, phylogenetic embedding only
(a la Strydom \emph{et al.} (2021a)), niche embedding only (Gravel
\emph{et al.} 2019), and all pairwise combinations of those constituent
models. After validating each model and selecting the best performing
model, we then predict how these distributions of each of these species
will change under the CMIP6 consensus climate forecast (Karger \emph{et
al.} 2017), and then finally quantify the reduction in spatial between
species for which there is a predicted interaction.

>>>>

As the data we have is spatially sparse and likely to contain many
interaction ``false-negatives'' (Strydom \emph{et al.} 2021b), we begin
by predicting a metaweb of interactions across Colorado as they exist
\emph{in the present}. We do this using a set of candidate interaction
prediction models: relative abundance only, phylogenetic embedding only
(a la Strydom \emph{et al.} (2021a)), niche embedding only (Gravel
\emph{et al.} 2019), and all pairwise combinations of those constituent
models. After validating and selecting the best performing model, we
then predict how these distributions of each of these species will
change under the CMIP6 consensus climate forecast (Karger \emph{et al.}
2017), and then finally quantify the reduction in spatial between
species for which there is a predicted interaction.
